Deterministic and statistical truncated KdV models for anomalous waves induced by abrupt depth change

### 2018-09-05 LatexNotes/Notes.tex
NM

Now, figures \ref{thetaplot}--\ref{match_micro} show results obtained by satisfying the matching condition \eqref{statmatch} using the algorithm described in \ref{sec_match}. In these tests, we use $\Lambda = 8$ and the provisional number of samples is $10^8$ (the number of accepted samples will be much lower). We also fix $E_0 = 4$ and $D_0 = 0.5$.

First, Fig.~\ref{thetaplot} shows, for given values of $\theta^-$, the corresponding values of $\theta^+$ as determined by the matching condition. For one, $\theta^- = 0$ corresponds to $\theta^+ = 0$ which is a good sanity check. Second, notice that the signs of $\theta^-$ and $\theta^+$ always agree, which is a good thing. The relationship is not a simply linear one, as the curvature is significant.

@@

%^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
\begin{figure}%[htbp]
\begin{center}
\includegraphics[width = 0.55 \textwidth]{thetaplot}
\caption{For given values of $\theta^-$, we compute $\theta^+$ to satisfy the matching condition.}
\label{thetaplot}
\end{center}
\end{figure}
 %^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^

>>>>

Now, figures \ref{match_theta}--\ref{match_micro} show results obtained by satisfying the matching condition \eqref{statmatch} using the algorithm described in \ref{sec_match}. In these tests, we use $\Lambda = 8$ and the provisional number of samples is $10^8$ (the number of accepted samples will be much lower). We also fix $E_0 = 4$ and $D_0 = 0.5$.

First, Fig.~\ref{match_theta} shows, for given values of $\theta^-$, the corresponding values of $\theta^+$ as determined by the matching condition. For one, $\theta^- = 0$ corresponds to $\theta^+ = 0$ which is a good sanity check. Second, notice that the signs of $\theta^-$ and $\theta^+$ always agree, which is a good thing. The relationship is not a simply linear one, as the curvature is significant.

@@

Little remark for the very careful reader: the plot in Fig. \ref{match_theta} is out of date (used $\Lambda=16$) and is not consistent with Figs.~\ref{matchH} and \ref{match_micro} (which used $\Lambda = 8$).

%^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
\begin{figure}%[htbp]
\begin{center}
\includegraphics[width = 0.55 \textwidth]{match_theta}
\caption{For given values of $\theta^-$, we compute $\theta^+$ to satisfy the matching condition.}
\label{match_theta}
\end{center}
\end{figure}
 %^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^
